---
format:
  pdf:
    documentclass: article
    keep-tex: true
    latex_engine: xelatex
    toc: false
    number-sections: false
    papersize: a4
    geometry:
      - top=14mm
      - left=15mm
      - right=15mm
      - bottom=20mm
      - heightrounded
    linestretch: 0.95
    fontfamily: libertine
    fontsize: 12pt
    include-in-header: cv-header.tex
    include-before-body: cv-info.tex
execute:
  echo: false
  warning: false
  message: false
draft: true
---

```{r}
# https://github.com/jhelvy/cv
# https://github.com/acbass49/CV_Quarto/
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(pander)
source("../code/cv.R")

cv_url <- "https://docs.google.com/spreadsheets/d/1ecqMkclPn-lhzgGHw2UTueiKkjTxuoAvJjpFKs3Jtm4/edit?usp=sharing"
```


\begin{large}{\bf EDUCATION}
  \vspace{3pt}
  \hrule
\end{large}

```{r}
cv_edu_raw <- read_sheet(ss = cv_url, sheet = "edu")
cv_edu_raw |>
  make_table(colwidths = c(12, 6, 82))
```

\begin{large}{\bf EMPLOYMENT HISTORY}
  \vspace{3pt}
  \hrule
\end{large}

```{r}
cv_employ_raw <- read_sheet(ss = cv_url, sheet = "employ")
cv_employ_raw |>
  mutate(job = paste0(job, ", ", aff)) |> 
  select(date, job) |> 
  make_table(colwidths = c(12, 88))
```

\begin{large}{\bf GRANTS}
  \vspace{3pt}
  \hrule
\end{large}

```{r}
cv_grants_raw <- read_sheet(ss = cv_url, sheet = "grants")

cv_grants <- cv_grants_raw |>
  mutate(
    outcome_year = year(outcome),
    my_role = factor(my_role, levels = c("PI", "Co-PI", "Co-I")),
    currency_symbol = case_when(currency == "dollars" ~ "$", currency == "pounds" ~ "\u00A3"),
    budget_total_formatted = paste0(currency_symbol, format(budget_total, big.mark = ",")),
    budget_my_formatted = paste0(currency_symbol, format(budget_my, big.mark = ",")),
    budget_total_usd_formatted = paste0("$", format(budget_total_usd, big.mark = ",", trim = T)),
    budget_my_usd_formatted = paste0("$", format(budget_my_usd, big.mark = ",", trim = T)),
    title = paste0(title, ". ", make_italic(paste0("Funding from ", sponsor)), ".")
  )

# The earliest year I've ever received funding
min_outcome_year <- min(cv_grants$outcome_year)

# Compute total grants received
total_grants <- sum(cv_grants$budget_total_usd)

total_grants_text <- paste0("$", format(total_grants, big.mark = ","))
```

I have successfully secured `r total_grants_text` in research grants since `r min_outcome_year`. Further details are provided below.

```{r}
cv_grants |>
  arrange(my_role, desc(outcome)) |>
  select(period, budget_total_usd_formatted, my_role, title) |>
  make_table(colwidths = c(12, 12, 7, 69), italic = T)
```

\begin{large}{\bf AWARDS}
  \vspace{3pt}
  \hrule
\end{large}

```{r}
cv_awards_raw <- read_sheet(ss = cv_url, sheet = "awards")
cv_awards_raw |>
  arrange(desc(year)) |> 
  select(date, description) |> 
  make_table(colwidths = c(12, 88))
```

\begin{large}{\bf RESEARCH TEAM}
  \vspace{3pt}
  \hrule
\end{large}

```{r}
cv_team_raw <- read_sheet(ss = cv_url, sheet = "team")

cv_team_raw |> 
  mutate(
    year = as.numeric(year),
    role = factor(role, levels = c("RA", "Intern")),
    next_dest = if_else(is.na(next_dest), "", next_dest)
  ) |> 
  arrange(role, next_dest != "", desc(year)) |> 
  select(period, role, name, next_dest) |> 
  make_table(colwidths = c(12, 10, 30, 46), longtable = T, header = make_italic(c("Tenure", "Role", "Name", "Next destination")), italic = T)
```
\begin{large}{\bf POLICY ENGAGEMENT}
  \vspace{3pt}
  \hrule
\end{large}

```{r}
cv_policy_raw <- read_sheet(ss = cv_url, sheet = "policy")

cv_policy_raw |> 
  arrange(desc(date)) |> 
  make_table(colwidths = c(12, 88))
```

\begin{large}{\bf TEACHING}
  \vspace{3pt}
  \hrule
\end{large}

```{r}
cv_teaching_raw <- read_sheet(ss = cv_url, sheet = "teaching")

cv_teaching <- cv_teaching_raw |> 
  mutate(
    name = paste0(make_italic(name), "\\newline ", note, ". ", make_url(website)),
    attd = as.character(attd)
  )
```

\textbf{Workshops}

```{r}
cv_teaching |> 
  filter(type == "workshop") |> 
  arrange(desc(year)) |> 
  select(date, attd, name) |> 
  make_table(colwidths = c(12, 10, 78), header = make_italic(c("Date", "Attendees", "Name")), italic = T, newline = T, url = T)
```

\textbf{Courses}

```{r}
cv_teaching |> 
  filter(type == "course") |> 
  arrange(desc(year)) |> 
  select(date, attd, name) |> 
  make_table(colwidths = c(12, 10, 78), header = make_italic(c("Date", "Attendees", "Name")), italic = T, newline = T, url = T)
```

\begin{large}{\bf SOFTWARE}
  \vspace{3pt}
  \hrule
\end{large}

```{r}
#| results: asis

cv_software_raw <- read_sheet(ss = cv_url, sheet = "software")

cv_software <- cv_software_raw |> 
  arrange(desc(year)) |> 
  mutate(
    # Bold my name
    author = str_replace_all(author, "T Ong", "**T Ong**"),
    software_text = paste0(author, " (", year, "). *", name, ": ", summary, "*. [", url_github, "](", url_github, ").")
  )

pandoc.list(cv_software$software_text, style = "ordered")
```


