% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
  a4paper,
]{article}
\usepackage{xcolor}
\usepackage[top=14mm,left=15mm,right=15mm,bottom=20mm,heightrounded]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage[]{libertine}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{setspace}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


% Set spacing between rows in tables
\renewcommand{\arraystretch}{1.35}

% Headers and footers
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}

% Sets both header and footer to nothing
\fancyhf{}
% Remove the top horizontal rule
\renewcommand{\headrulewidth}{0pt}

% When did this CV updated
\fancyfoot[L]{\footnotesize\emph{Updated \today}}
\fancyfoot[R]{Page \thepage\ of \pageref*{LastPage}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\author{}
\date{}
\begin{document}

\begin{huge}\begin{center}{\bf Thinh Ong}\end{center}\end{huge}
\begin{center}\href{mailto::ongphucthinh@gmail.com}{ongphucthinh@gmail.com} ∙ \href{https://drthinhong.com/}{Website} ∙ \href{https://www.linkedin.com/in/thinh-ong/}{LinkedIn}
\end{center}
\vspace{5pt}


\setstretch{0.95}
\begin{large}{\bf EDUCATION}
  \vspace{3pt}
  \hrule
\end{large}

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{10.2mm}>{\raggedright\arraybackslash}p{139.4mm}}

2022-2026 & PhD & University of Oxford, United Kingdom\\
2012-2018 & MD & University of Medicine and Pharmacy at Ho Chi Minh City, Vietnam\\

\end{tabu}

\begin{large}{\bf EMPLOYMENT HISTORY}
  \vspace{3pt}
  \hrule
\end{large}

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{149.6mm}}

2021-2022 & Research assistant, Mathematical Modelling Group, Oxford University Clinical Research Unit, Vietnam\\
2020-2021 & Editorial assistant, MedPharmRes, University of Medicine and Pharmacy at Ho Chi Minh City, Vietnam\\
2019-2020 & Research intern, Cancer Epigenetics Lab, Garvan Institute of Medical Research, Australia\\
2018-2023 & Biostatistical consultant, Infertility Department, Tu Du Hospital, Vietnam\\

\end{tabu}

\begin{large}{\bf GRANTS}
  \vspace{3pt}
  \hrule
\end{large}

I have successfully secured \$237,930 in research grants since 2022.
Further details are provided below.

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{11.9mm}>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{117.3mm}}

2025-2026 & PI & \$55,456 & \textit{Understanding how immunisation inequities drive measles outbreaks}. Funding from University of Oxford's internal 'Improving Equitable Access to Healthcare Pump Priming'.\\
2024-2025 & PI & \$27,694 & \textit{Modelling measles and hand-foot-mouth disease transmission dynamics in Ho Chi Minh city}. Funding from OUCRU's Programme Scientific Committee.\\
2023-2025 & PI & \$29,961 & \textit{The impacts of 15-month disruption in childhood vaccination programme on vaccination coverage and seroprevalence in Ho Chi Minh city}. Funding from OUCRU's Programme Scientific Committee.\\
2022-2024 & PI & \$20,437 & \textit{An R package for modelling infectious disease parameters based on serological and social contact data}. Funding from OUCRU's Programme Scientific Committee.\\
2024-2025 & Co-I & \$104,382 & \textit{Research cultures in Southeast Asia}. Funding from Wellcome.\\

\end{tabu}

\begin{large}{\bf AWARDS}
  \vspace{3pt}
  \hrule
\end{large}

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{149.6mm}}

2022-2026 & PhD Studentship: OUCRU \& NDM Tropical Network Fund (University of Oxford)\\
2019 & Outstanding Presentation, 36th Science \& Technology Conference, Ho Chi Minh City, Vietnam\\
2018 & Highest GPA in the 6-year medical doctor programme (highest in school history)\\
2018 & Highest dissertation score\\
2013-2018 & Annual highest GPA award\\

\end{tabu}

\begin{large}{\bf RESEARCH TEAM}
  \vspace{3pt}
  \hrule
\end{large}

\begin{longtabu} to \linewidth {>{\raggedright\arraybackslash}p{20.8163265306122mm}>{\raggedright\arraybackslash}p{17.3469387755102mm}>{\raggedright\arraybackslash}p{52.0408163265306mm}>{\raggedright\arraybackslash}p{79.7959183673469mm}}

\textit{Tenure} & \textit{Role} & \textit{Name} & \textit{Next destination}\\

2024-2026 & RA & Pham Nguyen The Nguyen & MPH programme at National Cancer Center Graduate School of Cancer Science and Policy\\
2023-2026 & RA & Phan Truong Quynh Anh & PhD programme at University of Oxford\\
2022-2023 & RA & Huynh Ngoc Tuyen & PhD programme at University of Oxford\\
2024 & Intern & Nguyen Thanh Lam & MPH programme at University of Caen Normandie\\
2024 & Intern & Julian Hough & BSc programme at Princeton University\\
\addlinespace
2024 & Intern & Huynh Xuan Loc & PhD programme at Boston University\\

\end{longtabu}

\begin{large}{\bf POLICY ENGAGEMENT}
  \vspace{3pt}
  \hrule
\end{large}

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{149.6mm}}

2024-2025 & Evaluated the city-wide infectious disease surveillance system\\
2024-2025 & Led the benchmarking and selection of algorithms for defining epidemic thresholds\\
2024 & Developed a surveillance dashboard tracking time-varying reproduction numbers to enhance CDC's response capabilities\\
2024 & Authored a rapid measles seroprevalence report to advise the Department of Health during an active outbreak\\

\end{tabu}

\begin{large}{\bf TEACHING}
  \vspace{3pt}
  \hrule
\end{large}

\textbf{Modelling}

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{17mm}>{\raggedright\arraybackslash}p{132.6mm}}

\textit{Date} & \textit{Attendees} & \textit{}\\

2025 & 30 & \textit{Modelling and Analysis of Serological Data: An Introductory Short Course}\newline Teaching assistant for a course jointly developed by MRC Centre for Global Infectious Disease Analysis, Imperial College London and National University of Singapore. Venue: Oxford University Clinical Research Unit. \url{}\\
2024-2025 & 15 & \textit{Infectious disease modelling for babies}\newline Methodologies for mathematical models of infectious diseases. Venue: HCMC's Center for Disease Control. \url{https://drthinhong.com/idm4b}\\
2023 & 60 & \textit{Introduction to mathematical models for controlling infectious diseases}\newline Developing basic compartmental models and the use of reproduction numbers. Venue: HCMC's Center for Disease Control. \url{https://lampk.github.io/IDMIntro}\\

\end{tabu}

\textbf{Others}

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{17mm}>{\raggedright\arraybackslash}p{132.6mm}}

\textit{Date} & \textit{Attendees} & \textit{}\\

2025 & 20 & \textit{Academic writing for babies}\newline Academic writing skills for early-career researchers. Venue: HCMC's Center for Disease Control. \url{}\\
2024-2025 & 10 & \textit{R café}\newline Fortnightly reproducibility in research classes. Venue: Oxford University Clinical Research Unit, HCMC's Center for Disease Control. \url{https://oucru-modelling.github.io/R-cafe-materials}\\
2024 & 40 & \textit{R for babies}\newline Monthly practical R programming classes. Venue: HCMC's Center for Disease Control. \url{https://drthinhong.com/r4babies}\\

\end{tabu}

\textbf{Seminars}

\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{20.4mm}>{\raggedright\arraybackslash}p{17mm}>{\raggedright\arraybackslash}p{132.6mm}}

\textit{Date} & \textit{Attendees} & \textit{}\\

2024 & 40 & \textit{Is this a good journal?}\newline Training on identifying trustworthy scientific journals. Venue: HCMC's Center for Disease Control. \url{}\\

\end{tabu}

\begin{large}{\bf SOFTWARE}
  \vspace{3pt}
  \hrule
\end{large}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Ong T}, Phan TQA, Ha ML, Choisy M (2025). \emph{denim:
  Construct and simulate deterministic discrete-time compartmental
  models with customisable dwell time distributions}.
  \url{https://thinhong.github.io/denim}.
\item
  Phan TQA, Pham NTN, Bui TL, Huynh NT, Choisy M, \textbf{Ong T} (2025).
  \emph{serosv: Analyse serological data and estimate infectious
  diseases parameters}. \url{https://oucru-modelling.github.io/serosv}.
\item
  Khuong QL, Pham NTN, \textbf{Ong T}, Getz K (2025). \emph{tvmedg:
  Causal mediation analysis using g-computation}.
  \url{https://causalepi.github.io/tvmedg/}.
\item
  Luu PL, \textbf{Ong T}, Loc TTH, Lam D, Pidsley R, Stirzaker C, Clark
  SJ (2021). \emph{MethPanel: Analyse multiplex bisulphite PCR
  sequencing to assess DNA methylation biomarker panels for disease
  detection}. \url{https://github.com/thinhong/MethPanel}.
\item
  Khuong QL, \textbf{Ong T}, Hoang VM (2020). \emph{hss: Estimate sample
  size for health study designs}.
  \url{https://thinhong.shinyapps.io/samplesize}.
\item
  Luu PL, \textbf{Ong T}, Dinh TP, Clark SJ (2020). \emph{Lifted:
  Enhance genome conversion robustness during reference assembly
  updates}. \url{https://github.com/thinhong/Lifted}.
\end{enumerate}

\begin{large}{\bf PUBLICATIONS}
  \vspace{3pt}
  \hrule
\end{large}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Huynh TM, \textbf{Ong T}, Tran DT, Quach DT, Vo TD.
  Neutrophil-C-reactive protein index as a novel prognostic tool for
  acute pancreatitis in resource-constrained settings. International
  Journal of Surgery. NA;112(2):3297.
  doi:\url{https://doi.org/10.1097/JS9.0000000000003846}
\item
  Huynh TM, \textbf{Ong T}, Gautam N, Nguyen HS. Refining
  intergenerational MASLD risk: are measurement and mediation shaping
  the signal?. Gut. 2026;: .
  doi:\url{https://doi.org/10.1136/gutjnl-2026-338664}
\item
  Huynh T, \textbf{Ong T}. Are S100A7 protein and V-set and
  immunoglobulin domain--containing 4 specific and robust early markers
  of severe acute pancreatitis?. Polish Archives of Internal Medicine.
  2026;: . doi:\url{https://doi.org/10.20452/pamw.17238}
\item
  Nguyen QD, \textbf{Ong T}P, Truong LTT, Trinh TH, Le HN, Do LAH, Huynh
  J. High vulnerability of infants under 6~months of age in Vietnam's
  measles outbreak. Vaccine. 2026;77: 128375.
  doi:\url{https://doi.org/10.1016/j.vaccine.2026.128375}
\item
  Huynh TM, \textbf{Ong T}. PancreaSure: Ready for Real-World PDAC
  Surveillance or Still Limited to a Highly Selected Cohort?.
  Gastroenterology. 2026;0(0):.
  doi:\url{https://doi.org/10.1053/j.gastro.2026.01.049}
\item
  \textbf{Ong T}P, Phan ATQ, Ha LM, Choisy M. denim: An R package for
  deterministic compartmental models with flexible dwell-time
  distributions. Methods in Ecology and Evolution. NA;17(4):1060-1068.
  doi:\url{https://doi.org/10.1111/2041-210x.70256}
\item
  \textbf{Ong T}, Thuy CT, Tam NH, Nga LH, Uyen NTV, Lan TTT, Tran A,
  Diem LTK, Khang HP, Dung DTX, Chuong LN, Tam NHT, Giang VC, Cam TTB,
  Anh HTN, Thu PTM, Man DNH, Dung NT, Tung NLN, Phat HH, Toan LM, Lam
  NT, Nguyen PNT, Nhung HN, Thanh TT, Chau NVV, Thuong TC, Thwaites G,
  Thwaites CL, Choisy M, Tan LV. Detection of Immunity Gap before
  Measles Outbreak, Ho Chi Minh City, Vietnam, 2024. Emerging Infectious
  Diseases. 2025;31(10):.
  doi:\url{https://doi.org/10.3201/eid3110.250234}
\item
  Phi HD, Ca TN, Oanh PM, Phong NT, \textbf{Ong T}, Nhung PTH. Impact of
  measles vaccination on disease severity and economic burden among
  children in northern Vietnam, 2017--2019. Vaccine: X. 2025;26: 100714.
  doi:\url{https://doi.org/10.1016/j.jvacx.2025.100714}
\item
  Leung K, Cook AR, Wu JT, McVernon J, Prem K, Jit M, Kingkaew P,
  Mukhopadhyay S, Isaranuwatchai W, Pan-ngum W, Teerawattananon Y, Huang
  A, Djaafara B, Sukmanee J, \textbf{Ong T}, Laemlak S, Chua VW,
  Rattanavipapong W, Dabak SV. Enhancing global health security
  responses through greater inclusion of the global south in infectious
  disease modelling. BMJ Glob Health. 2025;10(8):.
  doi:\url{https://doi.org/10.1136/bmjgh-2025-019111}
\item
  Le TMC, Duong KT, \textbf{Ong T}, Nguyen THN, Thai TCT, Nguyen TTH,
  Nguyen QA, Le QT, Pham NTN, Roque M, Alviggi C, Conforti A. O-187
  Individualized luteal phase support with intramuscular progesterone in
  patients with low serum progesterone on the day of frozen-thawed
  embryo transfer: a randomized clinical trial. Hum Reprod.
  2025;40(Supplement\_1):deaf097.187.
  doi:\url{https://doi.org/10.1093/humrep/deaf097.187}
\item
  Le TMC, Tran THD, Pham VP, Dang TL, Duong KT, Hua TT, Huynh TNT,
  Nguyen THN, Le QT, Nguyen BMN, Vo MT, \textbf{Ong T}, Pham NTN, Amorim
  CA. The first comparative study on the effectiveness of slow freezing
  and vitrification of human ovarian tissue by xenotransplantation model
  in Vietnam. J Assist Reprod Genet. 2025;42(5):1473-1484.
  doi:\url{https://doi.org/10.1007/s10815-025-03439-z}
\item
  Pham NML, \textbf{Ong T}, Vuong NL, Nguyen TTH. HLA Compatibility and
  Graft Survival Rates Among Related and Unrelated Donors in Renal
  Transplantation. Transplantation Proceedings. 2024;56(10):2163-2171.
  doi:\url{https://doi.org/10.1016/j.transproceed.2024.11.010}
\item
  Tran DM, \textbf{Ong T}, Cao TV, Pham QT, Do H, Phan PH, Choisy M,
  Pham NTH. Hospital-acquired infections and unvaccinated children due
  to chronic diseases: an investigation of the 2017--2019 measles
  outbreak in the northern region of Vietnam. BMC Infect Dis.
  2024;24(1):948. doi:\url{https://doi.org/10.1186/s12879-024-09816-w}
\item
  Le TMC, Duong KT, Nguyen QA, \textbf{Ong T}, Nguyen THN, Thai TCT, Le
  QT, Roque M, Alviggi C. Effectiveness of progesterone supplementation
  in women presenting low progesterone levels on the day of frozen
  embryo transfer: a randomised controlled trial. BMJ Open.
  2022;12(2):e057353.
  doi:\url{https://doi.org/10.1136/bmjopen-2021-057353}
\item
  Le Pham NM, \textbf{Ong T}, Vuong NL, Van Tran B, Nguyen TTH. HLA
  types and their association with end-stage renal disease in Vietnamese
  patients: A cross-sectional study. Medicine. 2022;101(48):e31856.
  doi:\url{https://doi.org/10.1097/MD.0000000000031856}
\item
  Le TMC, \textbf{Ong T}, Nguyen QA, Roque M. Fresh versus elective
  frozen embryo transfer: Cumulative live birth rates of 7,236 IVF
  cycles. JBRA Assist Reprod. 2022;26(3):450-459.
  doi:\url{https://doi.org/10.5935/1518-0557.20210094}
\item
  Le TTV, Vuong TTB, \textbf{Ong T}, Do MD. Allele frequency and the
  associations of HLA-DRB1 and HLA-DQB1 polymorphisms with pemphigus
  subtypes and disease severity. Medicine. 2022;101(7):e28855.
  doi:\url{https://doi.org/10.1097/MD.0000000000028855}
\item
  Vuong TBT, Do DM, \textbf{Ong T}, Thanh Le TV. HLA-DRB1 and DQB1
  genetic susceptibility to pemphigus vulgaris and pemphigus foliaceus
  in Vietnamese patients. Dermatol Reports. 2021;14(2):9286.
  doi:\url{https://doi.org/10.4081/dr.2021.9286}
\item
  Long KQ, Ngoc-Anh HT, Phuong NH, Tuyet-Hanh TT, Park K, Takeuchi M,
  Lam NT, Nga PTQ, Phuong-Anh L, Tuan LV, Bao TQ, \textbf{Ong T}, Huy
  NV, Lan VTH, Minh HV. Clustering Lifestyle Risk Behaviors among
  Vietnamese Adolescents and Roles of School: A Bayesian Multilevel
  Analysis of Global School-Based Student Health Survey 2019. The Lancet
  Regional Health -- Western Pacific. 2021;15: 100225.
  doi:\url{https://doi.org/10.1016/j.lanwpc.2021.100225}
\item
  Luu PL, \textbf{Ong T}, Loc TTH, Lam D, Pidsley R, Stirzaker C, Clark
  SJ. MethPanel: a parallel pipeline and interactive analysis tool for
  multiplex bisulphite PCR sequencing to assess DNA methylation
  biomarker panels for disease detection. Bioinformatics.
  2021;37(15):2198-2200.
  doi:\url{https://doi.org/10.1093/bioinformatics/btaa1060}
\item
  Huynh G, Tran TT, Do THT, Truong TTD, \textbf{Ong T}, Nguyen TNH, Pham
  LA. Diabetes-Related Distress Among People with Type 2 Diabetes in Ho
  Chi Minh City, Vietnam: Prevalence and Associated Factors. Diabetes,
  Metabolic Syndrome and Obesity. 2021;14: 683-690.
  doi:\url{https://doi.org/10.2147/DMSO.S297315}
\item
  Long KQ, \textbf{Ong T}, Thao TTK, Van Huy N, Lan VTH, Mai VQ, Van
  Minh H. Relationship between family functioning and health-related
  quality of life among methadone maintenance patients: a Bayesian
  approach. Qual Life Res. 2020;29(12):3333-3342.
  doi:\url{https://doi.org/10.1007/s11136-020-02598-z}
\item
  Luu PL, \textbf{Ong T}, Dinh TP, Clark SJ. Benchmark study comparing
  liftover tools for genome conversion of epigenome sequencing data. NAR
  Genomics and Bioinformatics. 2020;2(3):lqaa054.
  doi:\url{https://doi.org/10.1093/nargab/lqaa054}
\item
  Vu-Ngoc H, Uyen NCM, \textbf{Ong T}, Don LD, Danh NVT, Truc NTT, Vi
  VT, Vuong NL, Huy NT, Duong PDT. Analgesic effect of non-nutritive
  sucking in term neonates: A randomized controlled trial. Pediatrics \&
  Neonatology. 2020;61(1):106-113.
  doi:\url{https://doi.org/10.1016/j.pedneo.2019.07.003}
\item
  Dao Phuoc T, Khuong Quynh L, Vien Dang Khanh L, \textbf{Ong T}, Le Sy
  H, Le Ngoc T, Phung Khanh L. Clinical prognostic models for severe
  dengue: a systematic review protocol. Wellcome Open Res. 2019;4: 12.
  doi:\url{https://doi.org/10.12688/wellcomeopenres.15033.2}
\item
  \textbf{Ong T}, Anh HNV, Tung DT, Kien TG. Translation and
  cross-cultural adaptation of the Vietnamese version of the diabetes
  distress scale. MedPharmRes. 2018;2(3):5-11.
  doi:\url{https://doi.org/10.32895/UMP.MPR.2.3.5}
\item
  Huynh TM, Gautam N, \textbf{Ong T}. Is the selenium paradox in NAFLD a
  result of reverse causation and nutritional confounding?.
  International Journal of Surgery. NA;: 10.1097/JS9.0000000000005190.
  doi:\url{https://doi.org/10.1097/JS9.0000000000005190}
\end{enumerate}




\end{document}
